\vspace{-2cm}Formation Control of AAUSHIP

### 2015-11-15 paper.tex
Upd./rewritten a bit and removed fixme

@@

The model and simulation has proved to work when implemented on the AAUSHIP which results in a vessel that tracks a predetermined trajectory. This makes the basis for the further work of expanding the fleet of AAUSHIPS and implement the investigated control strategies and ending up with a successful digital mapping of the seabed in the Limfjord.

>>>>

Running the same setup as used in figure~\vref{fig:potform-po}, but with the addition of a few objects in the way of the paths it can be seen how the ships tries to evade the obstacles. The obstacles potential field is drawn as black circles. It shall be noted the plotted boundary is not a hard boundary, but only shows the radius whereby the potential field of the obstacles can affect other objects.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\linewidth]{fig/lawn-bar-formation-po}
  \caption{Same setups as in figure~\vref{fig:potform}, but with obstacles positioned on the pathways.}
  \label{fig:potform-po}
\end{figure}
On figure~\vref{fig:potform-po} there are placed two obstacles near each other on the first north going leg of the path. Here it is seen that two ships tries to gently diverge from the paths following near the boundary to the object, while it is seen that there is a ship going ``through'' the two objects influence zone. As describe previous, this is due to that the penalty for going around the entire set of obstacles is larger than crossing in between the objects. Because the two objects are offset a bit and about the same distance from the path it is clearly seen that the ship follows the minimum potential field through the set.

@@

The model and simulation has proved to work when implemented on the AAUSHIP which results in a vessel that can track a predetermined trajectory. This makes the basis for the further work of expanding the fleet of AAUSHIPS and implement the investigated control strategies on the fleet, ultimately ending up with a successful digital mapping of the seabed in the Limfjord in Denmark.

In this work the obstacles was regarded as point masses. An obvious extension of this work would be to expand the method to allow for polyhedral obstacles and then add the potential field of influence to this. This will immediately allow for better modelling of e.g. piers and other larger structures. 
solid in reality.
